\pkg{casebase}: An Alternative Framework For Survival Analysis and Comparison of Event Rates

### 2020-08-05 analysis/paper/paper.tex
update intro

From the perspective of clinicians and their patients, the most relevant
quantity is often the 5- or 10-year risk of having a certain event given
the patient's particular circumstances, and not the hazard ratio between
a treatment and control group. Therefore, to make sound clinical
decisions, it is important to accurately estimate the \emph{full} hazard
function, which can then be used to estimate the cumulative incidence
function (CIF). Since the parametric hazard is a smooth function of
time, the CIF and the survival function estimates also vary smoothly
over time.

@@

In this article, we present an \proglang{R} package that combines the
ideas of Hanley \& Miettinen into a simple interface. The purpose of the
\pkg{casebase} package is to provide practitioners with an easy-to-use
software tool to compute a patient's risk (or cumulative incidence) of
an event, conditional on a particular patient's covariate profile. Our
package retains the flexibility of case-base sampling and the familiar
interface of the \code{glm} function. In addition, we provide extensive
visualization tools.

@@

This report was generated on 2020-08-05 11:18:44 using the following
computational environment and dependencies:

>>>>

From the perspective of clinicians and their patients, the most relevant
quantity is often the 5- or 10-year risk of having a certain event given
the patient's particular circumstances, and not the hazard ratio between
a treatment and control group. Therefore, to make sound clinical
decisions, it is important to accurately estimate the \emph{full} hazard
function, which can then be used to estimate the cumulative incidence
function (CIF). Using a parametric estimator of the hazard function
leads to a smooth function of time; as a consequence, the CIF and the
survival function estimates also vary smoothly over time.

@@

Using the framework of logistic regression for analysing time-to-event
data opens the door to an extensive array of powerful modeling tools.
Indeed, lasso and elastic-net regression can then be used to select
variables that are associated with the hazard function. Logistic
regression can also be replaced by multinomial regression to analyse
data with multiple competing events.

In this article, we present an \proglang{R} package that combines the
ideas of Hanley \& Miettinen into a simple interface. The purpose of the
\pkg{casebase} package is to provide practitioners with an easy-to-use
software tool to compute a patient's risk (or cumulative incidence) of
an event, conditional on a particular patient's covariate profile. Our
package retains the flexibility of case-base sampling and the familiar
interface of the \code{glm} function. It also provides tools for
variable selection and competing-risk analysis. In addition, we provide
extensive visualization tools.

@@

This report was generated on 2020-08-05 11:28:49 using the following
computational environment and dependencies:
